README.md

### 2021-05-16 README.Rmd
journal issue 🌅

> Fernández-Pascual E (2021) [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science.*

>>>>

> Fernández-Pascual E (2021) [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science* 32, e12960.
